### 2018-10-21 Sections/encrypted_cloud_quantum_computing.tex
Bib: removed duplicates, fixed mistakes and typos, changed citations style

\dropcap{E}{xtremely} important to many high-performance data-processing applications is security, as proprietary or sensitive data may be being dealt with. To address this, there are two models for encrypted, outsourced quantum computation -- \textit{homomorphic encryption} \cite{???, gentry2009fully, van2010fully}\index{Homomorphic encryption} and \textit{blind quantum computation}\index{Blind quantum computation} \cite{???, bib:blind2, bib:blind3, bib:blind1, PhysRevLett.108.200502, bib:Morimae3486, bib:Morimae5460, bib:Morimae3966}.

>>>>

\dropcap{E}{xtremely} important to many high-performance data-processing applications is security, as proprietary or sensitive data may be being dealt with. To address this, there are two models for encrypted, outsourced quantum computation -- \textit{homomorphic encryption} \cite{bib:gentry2009fully, bib:van2010fully}\index{Homomorphic encryption} and \textit{blind quantum computation}\index{Blind quantum computation} \cite{bib:blind2, bib:broadbent2009universal, bib:barz2012demonstration, bib:PhysRevLett.108.200502, bib:Morimae3486, bib:Morimae5460, bib:Morimae5460}.

### 2018-10-21 Sections/essay_to_the_future_QKD.tex
Bib: removed duplicates, fixed mistakes and typos, changed citations style

A quantum repeater effectively needs to restore the quantum information without measuring it directly, and is extremely technologically challenging. Over optical fibre networks, the standard loss for 1550nm wavelength light is 0.2dB/km. Over long enough distances, this unavoidable loss will reduce the key-rate to a level of little practical relevance, therefore a ground-based solution would be to divide the entire channel into segments, where two partners exchange pairs of entangled photons and store it in a quantum memory\index{Quantum memory} \cite{bib:PhysRevLett.81.5932, bib:PhysRevA.59.169}.

>>>>

A quantum repeater effectively needs to restore the quantum information without measuring it directly, and is extremely technologically challenging. Over optical fibre networks, the standard loss for 1550nm wavelength light is 0.2dB/km. Over long enough distances, this unavoidable loss will reduce the key-rate to a level of little practical relevance, therefore a ground-based solution would be to divide the entire channel into segments, where two partners exchange pairs of entangled photons and store it in a quantum memory\index{Quantum memory} \cite{bib:BDCZ98, bib:dur98}.

### 2018-10-21 Sections/models_for_quantum_computation.tex
Bib: removed duplicates, fixed mistakes and typos, changed citations style

The cluster state formalism has proven very useful, enabling the development of models for linear optics quantum computing (Sec.~\ref{sec:KLM_univ}), orders of magnitude more efficient than the originally proposed protocol. It has been found that bonding strategies -- i.e the order in which smaller clusters are fused into larger ones when using non-deterministic gates -- plays a major role in resource overhead, and much work has been performed on efficient preparation strategies for various topologies \cite{bib:Nielsen04, bib:BarrettKok05, bib:BrowneRudolph05, bib:BenjaminEisert05, bib:Gross06, bib:RohdeStratCS07, bib:Kieling06, bib:KielingRudolphEisert06, bib:RohdeBarrett07, bib:Kieling07, bib:Campbell07, bib:Campbell07b}.

>>>>

The cluster state formalism has proven very useful, enabling the development of models for linear optics quantum computing (Sec.~\ref{sec:KLM_univ}), orders of magnitude more efficient than the originally proposed protocol. It has been found that bonding strategies -- i.e the order in which smaller clusters are fused into larger ones when using non-deterministic gates -- plays a major role in resource overhead, and much work has been performed on efficient preparation strategies for various topologies \cite{bib:Nielsen04, bib:BarrettKok05, bib:BrowneRudolph05, bib:BenjaminEisert05, bib:Gross06, bib:RohdeBarrett07, bib:Kieling06, bib:KielingRudolphEisert06, bib:RohdeBarrett07, bib:Kieling07, bib:Campbell07, bib:Campbell07b}.

### 2018-10-21 Sections/protocols_for_the_quantum_internet.tex
typo
Mission statement added
Bib: removed duplicates, fixed mistakes and typos, changed citations style

A completely general detector can be modelled as a POVM\index{POVM},
\begin{align}
\hat\Pi_m = \sum_{n=0}^\infty P(m|n) \ket{n}\bra{n},	
\end{align}
where $P(m|n)$ is the conditional probability of measuring $m$ photons given $n$ incident photons. The POVM\index{POVM} is fully characterised by the conditional probabilities, which must be inferred from the specifics of the architecture. Alternately, a quantum process\index{Quantum processes} formalism can be constructed as,
\begin{align}
\mathcal{E}(\hat\rho) = \sum_{n=0}^\infty P(m|n) \hat{E}_n\hat\rho\hat{E}_n^\dag,	
\end{align}
where \mbox{$\hat{E}_n=\hat{E}_n^\dag=\ket{n}\bra{n}$} are the Kraus operators\index{Kraus operators}.

@@

\subsection{Error correction}\index{Quantum error correction}

@@

@@

Suppose Alice and Bob share an entangled pair. Quantum mechanics, specifically the very definition of entanglement itself, prohibits local operations performed by Alice and Bob from increasing the level of entanglement. However, if Alice and Bob share multiple pairs, they can perform an operation known as \textit{entanglement purification} or \textit{entanglement distillation}, whereby two lower-fidelity entangled pairs are consumed and projected onto a single entangled pair with higher fidelity \cite{bib:PRA_53_2046, bib:PRA_54_3824, bib:PRL_77_2818}. Such protocols will be extremely useful in protocols where achieving the highest possible degree of entanglement is paramount, for example when error thresholds must be achieved for the purpose of error-correction and fault-tolerance \cite{bib:NielsenChuang00}.

@@

The obvious approach to sending a qubit from Alice to Bob is to send a qubit from Alice to Bob (duh!). However, over long distances this may accrue impractical error rates, particularly losses. The other alternative is to employ the quantum state teleportation protocol (Sec.~\ref{sec:teleport}) to teleport the state between the two parties. However, this requires that Alice and Bob first share an entangled Bell pair, which must itself be distributed across the same distances. Entanglement swapping \cite{???, bib:PRL_71_4287} is the process of taking two Bell pairs, one held by each party, and swapping the entanglement between them such that the two parties share an entangled state. This procedure can be bootstrapped to progressively swap the entanglement over longer and longer distances, yielding \textit{quantum repeater networks} (Sec.~\ref{sec:rep_net}). The procedure for this protocol is shown in Alg.~\ref{alg:ent_swap} and Fig.~\ref{fig:ent_swap}

>>>>

A completely general detector can be modelled as a POVM\index{POVM},
\begin{align}
\hat\Pi_m = \sum_{n=0}^\infty P(m|n) \ket{n}\bra{n},	
\end{align}
where $P(m|n)$ is the conditional probability of measuring $m$ photons given $n$ incident photons. The POVM\index{POVM} is fully characterised by the conditional probabilities, which must be inferred from the specifics of the architecture. Alternately, a quantum process\index{Quantum processes} formalism can be constructed as,
\begin{align}
\mathcal{E}_m(\hat\rho) = \sum_{n=0}^\infty P(m|n) \hat{E}_n\hat\rho\hat{E}_n^\dag,	
\end{align}
where \mbox{$\hat{E}_n=\hat{E}_n^\dag=\ket{n}\bra{n}$} are the Kraus operators\index{Kraus operators}.

@@

\subsection{Error correction}\index{Quantum error correction (QEC)}

@@

\comment{Add stuff on properties required for cryptographic purposes.}

@@

Suppose Alice and Bob share an entangled pair. Quantum mechanics, specifically the very definition of entanglement itself, prohibits local operations performed by Alice and Bob from increasing the level of entanglement. However, if Alice and Bob share multiple pairs, they can perform an operation known as \textit{entanglement purification} or \textit{entanglement distillation}, whereby two lower-fidelity entangled pairs are consumed and projected onto a single entangled pair with higher fidelity \cite{bib:PRA_53_2046, bib:PRA_54_3824, bib:Deutsch96}. Such protocols will be extremely useful in protocols where achieving the highest possible degree of entanglement is paramount, for example when error thresholds must be achieved for the purpose of error-correction and fault-tolerance \cite{bib:NielsenChuang00}.

@@

The obvious approach to sending a qubit from Alice to Bob is to send a qubit from Alice to Bob (duh!). However, over long distances this may accrue impractical error rates, particularly losses. The other alternative is to employ the quantum state teleportation protocol (Sec.~\ref{sec:teleport}) to teleport the state between the two parties. However, this requires that Alice and Bob first share an entangled Bell pair, which must itself be distributed across the same distances. Entanglement swapping \cite{???, bib:PhysRevLett.75.4337} is the process of taking two Bell pairs, one held by each party, and swapping the entanglement between them such that the two parties share an entangled state. This procedure can be bootstrapped to progressively swap the entanglement over longer and longer distances, yielding \textit{quantum repeater networks} (Sec.~\ref{sec:rep_net}). The procedure for this protocol is shown in Alg.~\ref{alg:ent_swap} and Fig.~\ref{fig:ent_swap}

### 2018-10-21 Sections/state_of_the_art.tex
Bib: removed duplicates, fixed mistakes and typos, changed citations style

	A technique for the generation of high-intensity polarisation-entangled photon pairs. For the partial Bell state projection a 50:50 beamsplitter was employed. & \cite{bib:kwiat1995new, bib:Euro_25_559} \\

@@

In 2008, \cite{bib:PRL_101_080403} used three pairs of polarisation-entangled photons, and conducted two Bell state measurements to realise multistage entanglement swapping. \cite{bib:PRL_103_020501} demonstrated multi-particle entanglement swapping using a three-photon GHZ state. In 2013, \cite{bib:PRL_110_210403} demonstrated entanglement swapping between photons that never coexisted. In their experiment, entangled photons are not only separated spatially, but also temporally. In 2015, \cite{bib:PRL_114_100501} experimentally realised hybrid entanglement swapping between discrete- and CV optical systems.

@@

Starting with two entangled atom-photon pairs, we can project the two atomic qubits into a maximally entangled state by performing a Bell state measurement on the two photons \cite{bib:Nature_428_153, bib:PRL_96_030404}. In 2007, \cite{bib:Nature_449_68} entangled two trapped atomic ions separated 1m apart using entanglement swapping, exploiting interference between photons emitted by the ions. The fidelity of the states of the entangled ions was $0.63(3)$. In subsequent experiments \cite{bib:PRL_100_150404}, the ion-ion entanglement fidelity was improved to $0.81$. Similarly, \cite{bib:Nature_454_1098} entangled two atomic ensembles, each originally with a single emitted photon, by performing a joint Bell state measurement on the two single photons after they had passed through a 300m fibre-based communication channel. In 2015, \cite{bib:Nature_526_682} generated robust entanglement (estimated state fidelity of $0.92\pm0.03$) between the two distant spins by entanglement swapping in the scheme of \cite{bib:PRA_71_060310, bib:Nature_497_86}. Such a high fidelity is sufficient to successfully perform loophole-free Bell inequality tests.

Entanglement swapping is a core element of quantum repeaters, which is of great significance to realising long-distance quantum communication. At present, the maximum transmission distance that can be achieved by QKD is 400km \cite{bib:arxiv_1606.06821}. Therefore, the communication distance is still a bottleneck restricting the development of quantum communication. Quantum repeaters, proposed in 1998 \cite{bib:PRL_81_5932}, combine entanglement swapping and quantum memory, which provides a potential solution to this problem.

The first proposed practical quantum repeater architecture was proposed in 2001 by Duan, Lukin, Cirac \& Zoller (DLCZ) \cite{bib:DLCZ}, using atomic ensembles and linear optics. To increase the repeater count-rate, various protocols \cite{bib:RMP_83_33, bib:PRA_79_042340, bib:PRA_92_012307, bib:PRA_81_052311, bib:PRA_81_052329, bib:NP_6_777, bib:PRL_112_250501} have been proposed.

@@

Experimental demonstration of elementary segments of quantum repeaters were achieved by \cite{bib:Sc_316_1316, bib:Nat_454_1098}.

@@

Aside from photonic systems, techniques based on other physical systems have also been developed \cite{bib:NP_11_37, bib:Sc_337_72, bib:N_484_195, bib:N_497_86}. In general, to enable scaling up to repeaters with several links, many techniques need to be considerably improved and simplified, and it appears there is still a long way to go before building a first practical, long-distance quantum repeater.

@@

\begin{table*}[!htbp]
\caption{Developments in experimental entanglement purification.} \label{tab:ent_pur}
\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
	\hline
	Summary & References \& years \\
	\hline \hline
	An experimentally viable purification scheme, requiring only PBSs and post-selection, was proposed and demonstrated. The scheme was demonstrated again, using mixed states with fidelity of $0.75$ ($0.8$), which they were able to purify to $0.92$ ($0.94$), a major improvement. & \cite{bib:Nature_410_1067, bib:Nature_423_417} \\
	\hline
	A Bell experiment was performed using purified states. A state initially failing a Bell test successfully passed the test following entanglement purification. Unfortunately, the theoretical efficiency of the purification scheme is only $1/4$. & \cite{bib:PRL_94_040504, bib:Nature_410_1067} \\
	\hline
\end{tabular}
\end{table*}

@@

Multi-photon GHZ states based on SPDC \cite{bib:kwiat1995new} can be step-by-step constructed with two-photon entangled states. Here we take the four photon one as an example \cite{bib:pan2012multiphoton}. Assume that two SPDC sources emit two polarisation entangled states \mbox{$\frac{1}{2}(\ket{HH} + \ket{VV})^{\otimes 2}$}. After passing through the polarizing beam-splitter (PBS), only the superposition \mbox{$\frac{1}{\sqrt{2}}(\ket{HHHH} + \ket{VVVV})$}, which is a four-photon GHZ state, leads to fourfold coincidence. In 1999, the world's first multi-particle 3-photon entanglement was generated \cite{bib:bouwmeester1999observation, bib:pan2000experimental}. After that, Pan \textit{et al.} broke the records continuously, and realised 4- \cite{bib:zhao2003experimental}, 5- \cite{bib:zhao2004experimental}, 6- \cite{bib:lu2007experimental}, 8- \cite{bib:yao2012observation}, 10-photon entanglement \cite{bib:tenPhotEnt}, and 10-qubit hyper-entanglement with two degrees of freedom \cite{bib:gao2010experimental}.

>>>>

	A technique for the generation of high-intensity polarisation-entangled photon pairs. For the partial Bell state projection a 50:50 beamsplitter was employed. & \cite{bib:PhysRevLett.75.4337, bib:Euro_25_559} \\

@@

In 2008, \cite{bib:goebel08} used three pairs of polarisation-entangled photons, and conducted two Bell state measurements to realise multistage entanglement swapping. \cite{bib:PRL_103_020501} demonstrated multi-particle entanglement swapping using a three-photon GHZ state. In 2013, \cite{bib:PRL_110_210403} demonstrated entanglement swapping between photons that never coexisted. In their experiment, entangled photons are not only separated spatially, but also temporally. In 2015, \cite{bib:PRL_114_100501} experimentally realised hybrid entanglement swapping between discrete- and CV optical systems.

@@

Starting with two entangled atom-photon pairs, we can project the two atomic qubits into a maximally entangled state by performing a Bell state measurement on the two photons \cite{bib:Nature_428_153, bib:PRL_96_030404}. In 2007, \cite{bib:Nature_449_68} entangled two trapped atomic ions separated 1m apart using entanglement swapping, exploiting interference between photons emitted by the ions. The fidelity of the states of the entangled ions was $0.63(3)$. In subsequent experiments \cite{bib:PRL_100_150404}, the ion-ion entanglement fidelity was improved to $0.81$. Similarly, \cite{bib:Nature_454_1098} entangled two atomic ensembles, each originally with a single emitted photon, by performing a joint Bell state measurement on the two single photons after they had passed through a 300m fibre-based communication channel. In 2015, \cite{bib:hensen2015loophole} generated robust entanglement (estimated state fidelity of $0.92\pm0.03$) between the two distant spins by entanglement swapping in the scheme of \cite{bib:BarrettKok05, bib:Nature_497_86}. Such a high fidelity is sufficient to successfully perform loophole-free Bell inequality tests.

Entanglement swapping is a core element of quantum repeaters, which is of great significance to realising long-distance quantum communication. At present, the maximum transmission distance that can be achieved by QKD is 400km \cite{bib:arxiv_1606.06821}. Therefore, the communication distance is still a bottleneck restricting the development of quantum communication. Quantum repeaters, proposed in 1998 \cite{bib:BDCZ98}, combine entanglement swapping and quantum memory, which provides a potential solution to this problem.

The first proposed practical quantum repeater architecture was proposed in 2001 by Duan, Lukin, Cirac \& Zoller (DLCZ) \cite{bib:Duan01}, using atomic ensembles and linear optics. To increase the repeater count-rate, various protocols \cite{bib:RMP_83_33, bib:PRA_79_042340, bib:PRA_92_012307, bib:PRA_81_052311, bib:PRA_81_052329, bib:NP_6_777, bib:MKLLJ14} have been proposed.

@@

Experimental demonstration of elementary segments of quantum repeaters were achieved by \cite{bib:Sc_316_1316, bib:Nature_454_1098}.

@@

Aside from photonic systems, techniques based on other physical systems have also been developed \cite{bib:NP_11_37, bib:Sc_337_72, bib:N_484_195, bib:bernien2013heralded}. In general, to enable scaling up to repeaters with several links, many techniques need to be considerably improved and simplified, and it appears there is still a long way to go before building a first practical, long-distance quantum repeater.

@@

\begin{table*}[!htbp]
\caption{Developments in experimental entanglement purification.} \label{tab:ent_pur}
\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
	\hline
	Summary & References \& years \\
	\hline \hline
	An experimentally viable purification scheme, requiring only PBSs and post-selection, was proposed and demonstrated. The scheme was demonstrated again, using mixed states with fidelity of $0.75$ ($0.8$), which they were able to purify to $0.92$ ($0.94$), a major improvement. & \cite{bib:Pan01, bib:Pan03} \\
	\hline
	A Bell experiment was performed using purified states. A state initially failing a Bell test successfully passed the test following entanglement purification. Unfortunately, the theoretical efficiency of the purification scheme is only $1/4$. & \cite{bib:PRL_94_040504, bib:Pan01} \\
	\hline
\end{tabular}
\end{table*}

@@

Multi-photon GHZ states based on SPDC \cite{bib:PhysRevLett.75.4337} can be step-by-step constructed with two-photon entangled states. Here we take the four photon one as an example \cite{bib:pan2012multiphoton}. Assume that two SPDC sources emit two polarisation entangled states \mbox{$\frac{1}{2}(\ket{HH} + \ket{VV})^{\otimes 2}$}. After passing through the polarizing beam-splitter (PBS), only the superposition \mbox{$\frac{1}{\sqrt{2}}(\ket{HHHH} + \ket{VVVV})$}, which is a four-photon GHZ state, leads to fourfold coincidence. In 1999, the world's first multi-particle 3-photon entanglement was generated \cite{bib:bouwmeester1999observation, bib:pan2000experimental}. After that, Pan \textit{et al.} broke the records continuously, and realised 4- \cite{bib:zhao2003experimental}, 5- \cite{bib:zhao2004experimental}, 6- \cite{bib:lu2007experimental}, 8- \cite{bib:yao2012observation}, 10-photon entanglement \cite{bib:tenPhotEnt}, and 10-qubit hyper-entanglement with two degrees of freedom \cite{bib:gao2010experimental}.
